# Brazil - 2016 Rio Olympics
<font size="6"><b> Analysis of Economic impacts on Brazil hosting Olympics by Regions </b></font>    

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(naniar)
library(zoo)
library(reactable)
library(scales)
library(ggridges)
library(viridis)
library(gganimate)
library(gifski)
```


```{r include=FALSE}
br_gdp <- read.csv('/Users/xiayunj/Desktop/datathon/datasets_full/Rio/brazil_gdp.csv')
br_ia <- read.csv('/Users/xiayunj/Desktop/datathon/datasets_full/Rio/brazil_international_arrivals.csv')
br_mi <- read.csv('/Users/xiayunj/Desktop/datathon/datasets_full/Rio/brazil_monthly_income.csv')
br_tj <- read.csv('/Users/xiayunj/Desktop/datathon/datasets_full/Rio/brazil_tourism_jobs.csv')
br_un <- read.csv('/Users/xiayunj/Desktop/datathon/datasets_full/Rio/brazil_unemployment.csv')
```

  
    
We can divide Brazil to 5 regions, where <b>Rio de Janeiro</b> is in the South-East Region.    
Reference: https://en.wikipedia.org/wiki/Regions_of_Brazil      
    
## Brazil GDP    
Source Data: `brazil_gdp.csv`      
     
<font size="5"><b> Brazil Regional GDP </b></font>      
```{r include=FALSE}
north <- c('Acre', 'Amapá', 'Amazonas', 'Pará', 'Rondônia', 'Roraima', 'Tocantins')
north_east <- c('Alagoas', 'Bahia', 'Ceará', 'Maranhão', 'Paraíba', 'Pernambuco', 'Piauí', 
                'Rio Grande do Norte', 'Sergipe')
mid_west <- c('Goiás', 'Mato Grosso', 'Mato Grosso do Sul', 'Distrito Federal')
south_east <- c('Espírito Santo', 'Minas Gerais', 'Rio de Janeiro', 'São Paulo')
south <- c('Paraná', 'Rio Grande do Sul', 'Santa Catarina')

for (i in 1:nrow(br_gdp)){
  if (br_gdp[i,'state'] %in% north){
    br_gdp[i,'larger_region'] <- 'North Region'
  } else if (br_gdp[i,'state'] %in% north_east){
    br_gdp[i,'larger_region'] <- 'North East Region'
  } else if (br_gdp[i,'state'] %in% mid_west){
    br_gdp[i,'larger_region'] <- 'Mid West Region'
  } else if (br_gdp[i,'state'] %in% south_east){
    br_gdp[i,'larger_region'] <- 'South East Region'
  } else {
    br_gdp[i,'larger_region'] <- 'South Region'
  }
}

```

```{r include=FALSE}
df_gdp <- br_gdp[,c('year','larger_region','value')] %>% 
  group_by(year, larger_region) %>% 
  summarise(gdp = sum(value))
df_gdp[,'gdp'] <- df_gdp$gdp/1000000000
```


```{r echo=FALSE, fig.height=5, fig.width=10}
ggplot(df_gdp, aes(year, gdp, color=larger_region)) + 
  geom_line() +
  geom_vline(xintercept = 2016, linetype="dashed", color = "red", size=1.5) +
  geom_text(aes(x = 2016, label = 'Rio Olympics', y = 2), colour = 'black', size = 4) +
  geom_vline(xintercept = 2009, linetype="dashed", color = "red", size=1.5) +
  geom_text(aes(x = 2009, label = 'Final Selection', y = 1), colour = 'black', size = 4) +
  ggtitle('Brazil GDP by Regions', subtitle = 'From 2002 to 2017') +
  labs(x = 'Year', y = 'GDP in trillions of Reals', color = 'Regions') +
  scale_x_continuous(breaks = seq(2002, 2017, 1)) +
  theme_gray(13)
```

<font size="5"><b> Brazil Regional GDP Increasing Rate from 2011 to 2017 </b></font>    
```{r echo=FALSE}
gdp_rate_temp <- df_gdp
gdp_rate <- data.frame('Year' = c('2003','2004','2005','2006','2007','2008','2009','2010',
                                  '2011','2012','2013','2014', '2015', '2016', '2017'))
```

```{r echo=FALSE}
for (i in 2003:2017){
  for (j in c('Mid West Region', 'North East Region',
              'North Region', 'South East Region', 'South Region')){
      gdp_rate[i-2002, j] <- round(as.numeric(
      (gdp_rate_temp[which(gdp_rate_temp$year == i & gdp_rate_temp$larger_region == j), 'gdp'] - 
      gdp_rate_temp[which(gdp_rate_temp$year == i-1 & gdp_rate_temp$larger_region == j), 'gdp']) /
      gdp_rate_temp[which(gdp_rate_temp$year == i-1 & gdp_rate_temp$larger_region == j), 'gdp']), 5)
              }
}
```

```{r echo=FALSE}
temp_col <- numeric(75)
for (i in 1:15){
  for (j in 2:6){
    temp_col <- c(temp_col, as.numeric(gdp_rate[i,j]))
  }
}
```

```{r echo=FALSE}
orange_pal <- function(x) rgb(colorRamp(c("#ffe4cc", "#ff9500"))(x), maxColorValue = 255)
reactable(
  gdp_rate,
  defaultColDef = colDef(
    align = 'center',
    headerStyle = list(background = "#D1E5FC"),
    format = colFormat(percent = TRUE, digits = 2),
    style = function(value) {
    if (!is.numeric(value)) {
      color <- "#A9D0FD"
      list(background = color)
    } else {
    normalized <- (value - min(temp_col)) / (max(temp_col) - min(temp_col))
    color <- orange_pal(normalized)
    list(background = color)
    }
  }
  ),
  bordered = TRUE,
  defaultPageSize = 5
)
```

<font size="4"><b> Observation: </b></font>     
1. South East Region of Brazil has much higher GDP than other 4 regions over years.    
2. Seems no significant increasing on Brazil regional GDP by 2016 Rio Olympics.    
3. Seems changes of regional GDP are unrelated to the Olympic games.    

From the time series plot for regional GDP over years, we find that year 2019 (the final selection year) seems to be a turning point for South East Region: after year 2019, GDP of South East Region increases faster than before. Therefore, we come up with our hypothesis that because of the success of placing a bid, South East Region then has a higher growth rate in GDP than other 4 regions.     
     
We want to test our hypothesis using two ANOVA tests: one is for the regional GDP growth rate from year 2003 to 2009; another one is for the regional GDP growth rate from year 2010 to 2017.   
    
<font size="4"><b> First ANOVA test on regional GDP from 2003 to 2009: </b></font>      
<font size="3"><b> Hypothesis: </b></font>       
$H_0$: The means of GDP increasing rate for the 5 regions from 2003 to 2009 are the same.    
$H_1$: Otherwise.     
Test: One-Way ANOVA     


```{r include=FALSE}
br_gdp_anova1_temp <- gdp_rate[1:7, -1]
br_gdp_anova2_temp <- gdp_rate[8:15, -1]

br_gdp_anova1 <- data.frame('region' = factor(), 'rate' = numeric())
for (i in 1:7){
  for (j in c('Mid West Region', 'North East Region',
              'North Region', 'South East Region', 'South Region')){
    br_gdp_anova1 <- br_gdp_anova1 %>% add_row(region = j, 
                                               rate = as.numeric(br_gdp_anova1_temp[i,j]))
  }
}

br_gdp_anova2 <- data.frame('region' = factor(), 'rate' = numeric())
for (i in 1:8){
  for (j in c('Mid West Region', 'North East Region',
              'North Region', 'South East Region', 'South Region')){
    br_gdp_anova2 <- br_gdp_anova2 %>% add_row(region = j, 
                                               rate = as.numeric(br_gdp_anova2_temp[i,j]))
  }
}
```

<font size="4"><b> Summary of the test: </b></font>       
```{r echo=FALSE}
model1 <- aov(rate~region, data = br_gdp_anova1)
summary(model1)
```
     
<font size="4"><b> Conclusion: </b></font>    
The p-value is 0.93, which shows that we fail to reject the null hypothesis.     
        
        
<font size="4"><b> First ANOVA test on regional GDP from 2010 to 2017: </b></font>      
<font size="3"><b> Hypothesis: </b></font>       
$H_0$: The means of GDP increasing rate for the 5 regions from 2010 to 2017 are the same.    
$H_1$: Otherwise.     
Test: One-Way ANOVA     
   
<font size="4"><b> Summary of the test: </b></font>       
```{r echo=FALSE}
model2 <- aov(rate~region, data = br_gdp_anova2)
summary(model2)
```

<font size="4"><b> Conclusion: </b></font>    
The p-value is 0.881, which shows that we fail to reject the null hypothesis.     
Therefore, for both tests, we fail to reject the null hypothesis. That is, we cannot say that the mean GDP growth rate for each of the 5 regions has significant difference. This also shows that the event of Olympic games does not impact on the GDP growth rate for regions in Brazil differenly.     


## Brazil Monthly Income  
Source Data: `brazil_monthly_income.csv`, `brazil_unemployment.csv`     
       
<font size="5"><b> Monthly Income Distribution </b></font>   
   
    
```{r include=FALSE}
#Note: There are some missing values in the raw data table. We choose to drop them. 
for (i in 1:nrow(br_mi)){
  if (br_mi[i,'state'] %in% north){
    br_mi[i,'larger_region'] <- 'North Region'
  } else if (br_mi[i,'state'] %in% north_east){
    br_mi[i,'larger_region'] <- 'North East Region'
  } else if (br_mi[i,'state'] %in% mid_west){
    br_mi[i,'larger_region'] <- 'Mid West Region'
  } else if (br_mi[i,'state'] %in% south_east){
    br_mi[i,'larger_region'] <- 'South East Region'
  } else {
    br_mi[i,'larger_region'] <- 'South Region'
  }
}
```


First, take a view at the distribution of monthly income for the entire country from 2012 to 2020:    
Note: We dropped missing values.   
```{r include=FALSE}
br_mi1 <- br_mi %>% drop_na()
```


```{r echo=FALSE, fig.height=5, fig.width=10}
ggplot(br_mi1, aes(x = as.factor(year), y = value)) + 
  geom_boxplot(fill = "#cc9a38", color = "#473e2c") + 
  ggtitle("Boxplots of Brazil Monthly Income ",
          subtitle = "From 2012 to 2020") +
  labs(x = "Year", y = "Monthly Income") +
  theme_grey(16) +
  theme(plot.title = element_text(face = "bold")) +
  theme(plot.subtitle = element_text(face = "bold", color = "grey35")) +
  theme(plot.caption = element_text(color = "grey68")) +
  scale_x_discrete(labels = c('2016'='2016 (Olympics)'))
```

From the Boxplots wo can find that the median of monthly income shows an increasing pattern from 2012 to 2020. However, there are higher outliers for each year, so we remove those higher outliers for further analysis on density estimation for better visualization.       
Higher Outlier definition: points above $Q_3 + (1.5\times \text{IQR})$, where $Q_3$ is the upper quartile and IQR is the Interquatile Range.    

```{r include=FALSE}
for (i in 2012:2020){
  temp_value <- br_mi1[which(br_mi1$year == i),]$value
  Q1 <- quantile(temp_value)[2]
  Q3 <- quantile(temp_value)[4]
  outlier <- Q3 + 1.5*(Q3-Q1)
  br_mi1 <- br_mi1[-which(br_mi1$year == i & br_mi1$value > outlier),]
}
```


```{r echo=FALSE, fig.height=6, fig.width=10, message=FALSE, warning=FALSE}
ggplot(br_mi1, aes(x = value, y = as.factor(year), fill = year))+
  geom_density_ridges_gradient(scale = 4, show.legend = FALSE) + 
  theme_ridges() +
  scale_y_discrete(expand = c(0.01, 0), labels = c('2016'='2016 \n (Olympics)')) +
  scale_x_continuous(expand = c(0.01, 0)) +
  labs(x = "Brazil Monthly Income",y = "Year") +
  ggtitle("Density estimation of Brazil Monthly Income", 
  subtitle = 'From 2012 to 2020 (outlier removed)') +
  theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5)) +
  scale_fill_viridis()
```

     
<font size="5"><b> Regional Monthly Income Distribution in the Olympics Year 2016 </b></font>    
```{r echo=FALSE, fig.height=7, fig.width=10}
ggplot(br_mi1[which(br_mi1$year == 2016),], aes(x = value, y = ..density..)) + 
  geom_histogram(bins = 20, colour = "#80593D", fill = "#9FC29F", boundary = 0) +
  geom_density(color = "#3D6480") + 
  facet_wrap(~larger_region) +
  ggtitle("2016 Brazil Monthly Income Distribution",
          subtitle = "by Regions (outlier removed)") +
  labs(x = "Monthly Income", y = 'Density') +
  theme(plot.title = element_text(face = "bold")) +
  theme(plot.subtitle = element_text(face = "bold", color = "grey35")) +
  theme(plot.caption = element_text(color = "grey68"))
```
   
<font size="4"><b> Observation: </b></font>    

Our hypothesis may be "hosting the Olympics can increase peoples' income in the hosting city/region". However, from this plot we find that the South East Region does not show a distribution of higher monthly income in year 2016.     


<font size="5"><b> Regional Average Monthly Income </b></font>     

Now we want to visualize the regional average monthly income. Here we keep the outliers because we are calculating the regional average for each year.   

```{r include=FALSE}
df_mi <- br_mi[, c('year','value','larger_region')] %>% 
  drop_na() %>%
  group_by(year, larger_region) %>% 
  summarise(monthly_income = mean(value))
```


```{r echo=FALSE, fig.height=5, fig.width=10}
ggplot(df_mi, aes(year, monthly_income, color=larger_region)) + 
  geom_line() +
  geom_vline(xintercept = 2016, linetype="dashed", color = "red", size=1.5) +
  geom_text(aes(x = 2016, label = 'Rio Olympics', y = 3000), colour = 'black', size = 4) +
  ggtitle('Brazil Average Monthly Income by Regions', 
          subtitle = 'From 2012 to 2020') +
  labs(x = 'Year', y = 'Average Monthly Income in Reals', color = 'Regions') +
  scale_x_continuous(breaks = seq(2012, 2020, 1)) +
  theme_gray(13)
```


```{r echo=FALSE}
mi_rate_temp <- df_mi
mi_rate <- data.frame('Year' = c('2013', '2014', '2015', '2016', '2017',
                                 '2018', '2019', '2020'))
```

```{r echo=FALSE}
for (i in 2013:2020){
  for (j in c('Mid West Region', 'North East Region',
              'North Region', 'South East Region', 'South Region')){
      mi_rate[i-2012, j] <- round(as.numeric(
      (mi_rate_temp[which(mi_rate_temp$year == i & 
                            mi_rate_temp$larger_region == j), 'monthly_income'] - 
      mi_rate_temp[which(mi_rate_temp$year == i-1 & 
                            mi_rate_temp$larger_region == j), 'monthly_income']) /
      mi_rate_temp[which(mi_rate_temp$year == i-1 & 
                            mi_rate_temp$larger_region == j), 'monthly_income']), 5)
              }
}
```

```{r echo=FALSE}
temp_col_mi <- numeric(40)
for (i in 1:8){
  for (j in 2:6){
    temp_col_mi <- c(temp_col_mi, as.numeric(mi_rate[i,j]))
  }
}
```


<font size="5"><b> Regional Monthly Income Increasing Rate from 2013 to 2020 </b></font>      
```{r echo=FALSE}
reactable(
  mi_rate,
  defaultColDef = colDef(
    align = 'center',
    headerStyle = list(background = "#D1E5FC"),
    format = colFormat(percent = TRUE, digits = 2),
    style = function(value) {
    if (!is.numeric(value)) {
      color <- "#A9D0FD"
      list(background = color)
    } else {
    normalized <- (value - min(temp_col_mi)) / (max(temp_col_mi) - min(temp_col_mi))
    color <- orange_pal(normalized)
    list(background = color)
    }
  }
  ),
  bordered = TRUE
)
```  

<font size="4"><b> Observation: </b></font>      
1. Seems no significant difference of increasing rate between the 5 regions around year 2016.    
2. For South East Region, the increasing rate in 2016 is lower than that in 2015. (Why?)   
   
## Brazil Unemployment Rate     
 
```{r include=FALSE}
for (i in 1:nrow(br_un)){
  if (br_un[i,'state'] %in% north){
    br_un[i,'larger_region'] <- 'North Region'
  } else if (br_un[i,'state'] %in% north_east){
    br_un[i,'larger_region'] <- 'North East Region'
  } else if (br_un[i,'state'] %in% mid_west){
    br_un[i,'larger_region'] <- 'Mid West Region'
  } else if (br_un[i,'state'] %in% south_east){
    br_un[i,'larger_region'] <- 'South East Region'
  } else {
    br_un[i,'larger_region'] <- 'South Region'
  }
}
```

```{r include=FALSE}
br_un_bar <- br_un[which(br_un$category != 'Outside the workforce' & br_un$year != 2020),
                   c('year','quarter','category','value','larger_region')] %>%
  group_by(year, quarter, category) %>%
  summarise(value = sum(value))

for (i in 1:nrow(br_un_bar)){
  y_temp <- br_un_bar$year[i]
  q_temp <- br_un_bar$quarter[i]
  un_temp <- br_un_bar[which(br_un_bar$year == y_temp & br_un_bar$quarter == q_temp &
                  br_un_bar$category == 'Workforce - Unemployed'), 'value']
  e_temp <- br_un_bar[which(br_un_bar$year == y_temp & br_un_bar$quarter == q_temp &
                  br_un_bar$category == 'Workforce - Employed'), 'value']
  if (br_un_bar$category[i] == 'Workforce - Unemployed'){
    br_un_bar[i,'rate'] <- un_temp/(un_temp+e_temp)
  } else {
    br_un_bar[i,'rate'] <- e_temp/(un_temp+e_temp)
  }
  br_un_bar[i,'work_force'] <- un_temp+e_temp
}

br_un_bar <- br_un_bar %>%
  group_by(year, category) %>%
  summarize(avg_rate = mean(rate)) 
```


```{r echo=FALSE, fig.height=6, fig.width=10, message=FALSE, warning=FALSE}
ggplot(br_un_bar, aes(x = as.factor(year), y = avg_rate, fill = category)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  ggtitle('Stacked Bar Chart of Average Brazil Unemployment/Employment Rate',
          subtitle = 'From 2012 to 2019') +
  labs(x = 'Rate', y = 'Year') +
  theme_gray(13) +
  scale_x_discrete(labels = c('2016'='2016 \n (Olympics)'))
```
      
From this plot we find that year 2017 has the highest average unemployment rate. Also, the average unemployment rate keeps increasing from 2015 to 2017.      
      

<font size="5"><b> Unemployment Rate by Regions </b></font>      
```{r include=FALSE}
#Calculate unemployment rate and work force for each quarter of each year (by region)  
df_un <- br_un[which(br_un$category != 'Outside the workforce'),
               c('year','quarter','category','value','larger_region')] %>% 
  group_by(year, quarter, category, larger_region) %>% 
  summarise(value = sum(value)) 
```

```{r include=FALSE}
for (i in 1:nrow(df_un)){
  y_temp <- df_un$year[i]
  q_temp <- df_un$quarter[i]
  r_temp <- df_un$larger_region[i]
  un_temp <- df_un[which(df_un$year == y_temp & df_un$quarter == q_temp & df_un$larger_region == r_temp &
                  df_un$category == 'Workforce - Unemployed'), 'value']
  e_temp <- df_un[which(df_un$year == y_temp & df_un$quarter == q_temp & df_un$larger_region == r_temp &
                  df_un$category == 'Workforce - Employed'), 'value']
  df_un[i,'unemployment_rate'] <- un_temp/(un_temp+e_temp)
  df_un[i,'work_force'] <- un_temp+e_temp
}
```


```{r include=FALSE}
df_un <- unique(subset(df_un, select=-c(category,value)))
```

 
```{r include=FALSE}
#Calculate average unemployment rate for each year (by region)  
df_un1 <- df_un %>%
  group_by(year, larger_region) %>% 
  summarise(avg_un_rate = mean(unemployment_rate))
```

```{r echo=FALSE, fig.height=5, fig.width=10, message=FALSE, warning=FALSE}
ggplot(df_un1[1:40,], aes(year, avg_un_rate, color=larger_region)) + 
  geom_line() +
  ggtitle('Brazil Average Yearly Unemployment Rate by Regions',
          subtitle = 'From 2012 to 2019') +
  labs(x = 'Year', y = 'Average Yearly Unemployment Rate', color = 'Regions') +
  scale_x_continuous(breaks = seq(2012, 2019, 1)) +
  theme_gray(13) +
  geom_vline(xintercept = 2016, linetype="dashed", color = "red", size=1.5) +
  geom_text(aes(x = 2016, label = 'Rio Olympics', y = 0.06), colour = 'black', size = 4)
```

<font size="5"><b> Unemployment Rate Increasing Rate by Regions from 2013 to 2019 </b></font>    
```{r echo=FALSE, message=FALSE, warning=FALSE}
un_rate_temp <- df_un1[1:40,]
un_rate <- data.frame('Year' = c('2013', '2014', '2015', '2016', '2017',
                                 '2018', '2019'))
```

```{r echo=FALSE}
for (i in 2013:2019){
  for (j in c('Mid West Region', 'North East Region',
              'North Region', 'South East Region', 'South Region')){
      un_rate[i-2012, j] <- round(as.numeric(
      (un_rate_temp[which(un_rate_temp$year == i & 
                            un_rate_temp$larger_region == j), 'avg_un_rate'] - 
      un_rate_temp[which(un_rate_temp$year == i-1 & 
                            un_rate_temp$larger_region == j), 'avg_un_rate']) /
      un_rate_temp[which(un_rate_temp$year == i-1 & 
                            un_rate_temp$larger_region == j), 'avg_un_rate']), 5)
              }
}
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
temp_col_un <- numeric(35)
for (i in 1:7){
  for (j in 2:6){
    temp_col_un <- c(temp_col_un, as.numeric(un_rate[i,j]))
  }
}
```

   
```{r echo=FALSE, message=FALSE, warning=FALSE}
reactable(
  un_rate,
  defaultColDef = colDef(
    align = 'center',
    headerStyle = list(background = "#D1E5FC"),
    format = colFormat(percent = TRUE, digits = 2),
    style = function(value) {
    if (!is.numeric(value)) {
      color <- "#A9D0FD"
      list(background = color)
    } else {
    normalized <- (value - min(temp_col_un)) / (max(temp_col_un) - min(temp_col_un))
    color <- orange_pal(normalized)
    list(background = color)
    }
  }
  ),
  bordered = TRUE
)
```  

<font size="4"><b> Obserevation: </b></font>      
Since 2014, the average unemployment rate keeps increasing for all of the 5 regions until 2017. The highest increasing rate appears at year 2016 which is the Olympics year for all of the 5 regions.    

       
## Brazil Tourism   
Source Data: `brazil_tourism_jobs.csv`    
```{r include=FALSE}
for (i in 1:nrow(br_tj)){
  if (br_tj[i,'state'] %in% north){
    br_tj[i,'larger_region'] <- 'North Region'
  } else if (br_tj[i,'state'] %in% north_east){
    br_tj[i,'larger_region'] <- 'North East Region'
  } else if (br_tj[i,'state'] %in% mid_west){
    br_tj[i,'larger_region'] <- 'Mid West Region'
  } else if (br_tj[i,'state'] %in% south_east){
    br_tj[i,'larger_region'] <- 'South East Region'
  } else {
    br_tj[i,'larger_region'] <- 'South Region'
  }
}
```

```{r include=FALSE}
df_tj <- br_tj %>% 
  group_by(year, month, larger_region) %>% 
  summarise(total_jobs = sum(jobs)) %>%
  group_by(year, larger_region) %>%
  summarise(avg_jobs = mean(total_jobs)/1000)
```

```{r echo=FALSE, fig.height=5, fig.width=10}
ggplot(df_tj, aes(year, avg_jobs, color=larger_region)) + 
  geom_line() +
  ggtitle('Brazil Average Yearly Tourism Jobs by Regions', 
          subtitle = 'From 2006 to 2018') +
  labs(x = 'Year', y = 'Average Yearly Tourism Jobs in Thousands', color = 'Regions') +
  scale_x_continuous(breaks = seq(2006, 2018, 1)) +
  theme_gray(13) +
  geom_vline(xintercept = 2016, linetype="dashed", color = "red", size=1.5) +
  geom_text(aes(x = 2016, label = 'Rio Olympics', y = 300), colour = 'black', size = 4)
```

<font size="5"><b> Brazil International Tourists </b></font>  
```{r include=FALSE}
df_ia <- br_ia %>%
  replace_with_na(replace = list(value = '')) %>%
  drop_na() %>%
  mutate(value = as.numeric(as.character(gsub(',','',value)))) %>%
  group_by(year, month) %>%
  summarize(value = sum(value)/1000)
```

```{r include=FALSE}
df_ia$Date <- as.yearmon(paste(df_ia$year, df_ia$month), "%Y %m")
```

```{r echo=FALSE, fig.height=5, fig.width=10}
ggplot(df_ia, aes(Date, value)) + 
  geom_line() +
  ggtitle('Brazil International Tourists from 1989 to 2018') +
  labs(x = 'Year', y = 'International Tourists in Thousands') +
  scale_x_continuous(breaks = seq(1989, 2018, 2)) +
  theme_gray(13)
```


## Interactive 


